Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-10 paper.tex
Gratuitously inherit from a prototypical drawing activity.

\subsection{Rule-based story modules}
\begin{figure}\small
\begin{verbatim}
{ world: { // id gives canonical URL for this module
    id: "/nell.laptop.org/chapters/alphabet-book"
    scene: "opening", // initial scene
  }, scenes: [
    { id: "opening", subject: "actors/princess",
      verb: "speak", object: "actors/user",
      text: "Hello! Would (o/2) like to hear a story?"
    },
    { id: "story-1",
      cond: rule`At(opening) && Event(Chat, Yes)`,
      subject: "actors/princess",
      verb: "speak", object: "actors/user",
      text: "Once upon a time..." },
    ...
    { id: "r-drawn",
      cond: rule`Event(Activity, DrawR)`,
      subject: "actors/princess",
      verb: "speak", object: "actors/user",
      text: "Very good, (o/3)!",
      action: js`startAnimation("r-runs")` },
    ...
  ], ... }
\end{verbatim}
\caption{Excerpt of story module.  JSON syntax has been extended with
quasiquote~\cite{quasiquote}.}\label{fig:rules}
\end{figure}
Narrative is the core of the Nell interface.  It is important that
Nell's story be modular and extensible.  We use a rule-based story
model with programmable conflict resolution to provide this ability.
Figure~\ref{fig:rules} shows an excerpt of the story module driving
the interaction described in the introduction to this paper.

>>>>

\subsection{Rule-based story modules}
\begin{figure}\small
\begin{verbatim}
{ world: { // id gives canonical URL for this module
    id: "/nell.laptop.org/chapters/alphabet-book",
    scene: "opening", // initial scene
    inherit_from: "/nell.laptop.org/core/drawing_activity",
  }, scenes: [
    { id: "opening", subject: "actors/princess",
      verb: "speak", object: "actors/user",
      text: "Hello! Would (o/2) like to hear a story?"
    },
    { id: "story-1",
      cond: rule`At(opening) && Event(Chat, Yes)`,
      subject: "actors/princess",
      verb: "speak", object: "actors/user",
      text: "Once upon a time..." },
    ...
    { id: "r-drawn",
      cond: rule`Event(Activity, DrawR)`,
      subject: "actors/princess",
      verb: "speak", object: "actors/user",
      text: "Very good, (o/3)!",
      action: js`startAnimation("r-runs")` },
    ...
  ], ... }
\end{verbatim}
\caption{Excerpt of story module.  JSON syntax has been extended with
quasiquote~\cite{quasiquote}.}\label{fig:rules}
\end{figure}
Narrative is the core of the Nell interface.  It is important that
Nell's story be modular and extensible.  We use a rule-based story
model with programmable conflict resolution to provide this ability.
Figure~\ref{fig:rules} shows an excerpt of the story module driving
the interaction described in the introduction to this paper.
